Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-26 sections/compiler.tex
concordization

\subsection{Concordization}
    Finch uses

>>>>

\subsection{Concordization}
    After wrapperization, all arrays are normalized to column-major ordering and
    the unrecognized expressions are left in the access expressions. At that
    point, we run a pass over the code to make the program concordant.

    We make expressions concordant by inserting loops with one iteration. For example, the following expression can be made concordant by adding a loop for the out of order access to \texttt{i}.
    \begin{minted}{julia}
        @finch begin
        for i = _
            for j = _
                for k = _
                    s[] += A[i, k, j]
                end
            end
        end
    \end{minted}

    \begin{minted}{julia}
        @finch begin
        for i = _
            for j = _
                for k = _
                    for l = _
                        if i == l #diagonal mask
                            s[] += A[l, k, j]
                        end
                    end
                end
            end
        end
    \end{minted}

    We can concordize unrecognized index expressions using a similar approach:

    \begin{minted}{julia}
        for i = _
            A[I[i]] += 1
        end
    \end{minted}

    \begin{minted}{julia}
        for i = _
            for j = _
                if j == I[i]
                    A[j] += 1
                end
            end
        end
    \end{minted}
